# Collaborating (`git fetch & merge (or pull)`)

**Key terms/commands:**

* **git fetch**: look at the changes that is in your remote repository Github. This commands download the changes into the `.git/` folder so you can compare changes to your local files, but it does not actually modify your files (i.e., files outside of the `.git/` folder). 

* **git merge**: implement the changes you have *fetched* into your local files. 

* **git pull**: `git fetch` + `git merge`. it is recommended that you fetch first, and check that you want to implement the changes, and then merge.


## Setup a fake collaborator, yourself in another directory :) 

Clone the **workdir** repo into your local computer but a different folder as if you have a collaborator

`git clone https://github.com/your_username/workdir.git ~/workdir_fake_collab`

```{r echo=F}
# copy workdir into fakedir using R code that is hidden
file.copy("~/workdir","~/workdir_fake_collab",recursive=TRUE)

# Change directory into workdir_fake_collab
knitr::opts_knit$set(root.dir="~/workdir_fake_collab")
```

Lets pretend you are the collaborator, and you will make some changes and push it to Github

```{bash}
cd ~/workdir_fake_collab

touch foofoo.txt

git add foofoo.txt

git commit -m "Add foofoo.txt"
```

Push this change to Github
```
git push origin master
```


Lets check what is in the current folder 

```{bash}
ls
```

Check what is on the workdir repository on Github. It should contain `foofoo.txt`

But what about the original `workdir` folder? 

```{bash}
cd  ~/workdir
ls
```

```{r, echo=F}
knitr::opts_knit$set(root.dir="~/workdir")
```

`foofoo.txt` should be missing. Now lets say you want to check what changes your collaborator made. 

## Implement the changes your fake collaborator made

**fetch** the changes your fake collaborator pushed to Github onto your local computer. 

`git fetch`

Here is an example output from running `git fetch`, exact details will vary.
```
remote: Enumerating objects: 4, done.
remote: Counting objects: 100% (4/4), done.
remote: Compressing objects: 100% (2/2), done.
remote: Total 3 (delta 0), reused 0 (delta 0), pack-reused 0
Unpacking objects: 100% (3/3), done.
From github.com:your_username/tmp
   d4a8d31..09aba9d  master     -> origin/master
```

NOTE that this does not change the files in your directory. But now you can use `git diff` to see what your collaborator has changed

`git diff master origin/master`

If you decided these are changes you want in your local directory (the origainl `workdir`)

`git merge`

## Notes {-}
* `git merge` returns message "Already up to date."
	+ `git merge` impelment the changes that were fetched by `git fetch`, so fetch first. 
* Will `git fetch` change my stuff? 
	+ Fetching does not change your local file until your pull. 

## BONUS - What is my remote? {-}
What is your remote? 

`git remote -v`

Adding a different remote

`git add remote [name] [url]`

Changing the URL of the remote (e.g., you change the remote repository)

`git remote set-url [name] [newurl]`


## Really collaborating on Github

* Adding collaborators in your Github repository
	+ Click **Settings**
	+ Click **Collaborators** and add them (they need to be on Github)
	
* More Advance way to collaborate (won't cover in detail)
	+ **fork** a repository you want to make changes 
	+ **git clone** it to your local computer
	+ Make changes, **git add**, **git commit** and **git push** it to your forked remote repo
	+ Make a [Pull Request](https://help.github.com/en/articles/creating-a-pull-request) in the original repository