# Collaborating (`git fetch & merge (or pull)`)

**Key terms/commands:**

* **git fetch**: look at the changes that is in your remote repository GitHub. This command download the changes into the `.git/` folder so you can compare changes to your local files, but it does not actually modify your files (i.e., files outside of the `.git/` folder). 

* **git merge**: implement the changes you have *fetched* into your local files. 

* **git pull**: `git fetch` + `git merge`. it is recommended that you fetch first, and check that you want to implement the changes, and then merge.


## Setup a fake collaborator, yourself in another directory :) 

Clone the **workdir** repo into your local computer but a different folder as if you have a collaborator

`git clone https://github.com/your_username/workdir.git ~/workdir_fake_collab`

```{r echo=F}
# copy workdir into fakedir using R code that is hidden
system("cp -r ~/workdir ~/workdir_fake_collab")

# Change directory into workdir_fake_collab
knitr::opts_knit$set(root.dir="~/workdir_fake_collab")
```

Let's pretend you are the collaborator, and you will make some changes and push it to GitHub. 
Here we go into the collab directory, make a new file `foofoo.txt`, then `add`/`commit` it. 

```{bash}
cd ~/workdir_fake_collab
touch foofoo.txt
git add foofoo.txt
git commit -m "Add foofoo.txt"
```

Push this change to GitHub

```{bash, eval = FALSE}
git push origin master
```

```
## Counting objects: 2, done.
## Delta compression using up to 8 threads.
## Compressing objects: 100% (2/2), done.
## Writing objects: 100% (2/2), 245 bytes | 245.00 KiB/s, done.
## Total 2 (delta 1), reused 0 (delta 0)
## remote: Resolving deltas: 100% (1/1), completed with 1 local object.
## To github.com:your_username/workdir.git
##    f9bed0e..7e740d1  master -> master
```

Lets check what is in the current folder 

```{bash}
ls
```

Check what is on the workdir repository on GitHub. It should contain `foofoo.txt`

But what about the original `workdir` folder? 

```{bash}
cd  ~/workdir
ls
```

```{r, echo=F}
knitr::opts_knit$set(root.dir="~/workdir")
```

`foofoo.txt` should be missing. Now let's say you want to check and incorporate the changes your collaborator made in your original folder. 

## Implement the changes your fake collaborator made

**fetch** the changes your fake collaborator pushed to GitHub onto your local computer. 

```{bash, eval = FALSE}
git fetch
```

Here is an example output from running `git fetch`, exact details will vary.
```
## remote: Enumerating objects: 3, done.
## remote: Counting objects: 100% (3/3), done.
## remote: Compressing objects: 100% (1/1), done.
## remote: Total 2 (delta 1), reused 2 (delta 1), pack-reused 0
## Unpacking objects: 100% (2/2), done.
## From github.com:your_username/workdir
##    7e740d1..5e3ff23  master     -> origin/master
```

NOTE that this does not change the files in your directory. But now you can use check to see what your collaborator has changed

```{bash, eval = F}
git diff master origin/master`
```

```
## diff --git a/foofoo.txt b/foofoo.txt
## new file mode 100644
## index 0000000..e69de29
```

If you decided these are changes you want in your local directory (the origainl `workdir`)

```{bash, eval = FALSE}
git merge
```

```
## Updating 7e740d1..5e3ff23
## Fast-forward
##  foofoo.txt | 0
##  1 file changed, 0 insertions(+), 0 deletions(-)
##  create mode 100644 foofoo.txt
```

## Notes {-}
* `git merge` returns message "Already up to date."
	+ `git merge` impelment the changes that were fetched by `git fetch`, so fetch first. 
* Will `git fetch` change my stuff? 
	+ Fetching does not change your local file until your pull. 

## BONUS - What is my remote? {-}
What is your remote? 

```{bash, eval = FALSE}
git remote -v
```

Adding a different remote

```{bash, eval = FALSE}
git add remote [name] [url]
```

Changing the URL of the remote (e.g., you change the remote repository)

```{bash, eval = FALSE}
git remote set-url [name] [newurl]
```

## Really collaborating on GitHub

* Adding collaborators in your GitHub repository
	+ Click **Settings**
	+ Click **Collaborators** and add them (they need to be on GitHub)
	
* More Advance way to collaborate (won't cover in detail)
	+ **fork** a repository you want to make changes 
	+ **git clone** it to your local computer
	+ Make changes, **git add**, **git commit** and **git push** it to your forked remote repo
	+ Make a [Pull Request](https://help.github.com/en/articles/creating-a-pull-request) in the original repository
	
***
**You have now `fetch` and `merge` changes from different people (or yourself on a different computer/folder)!**