# (PART) Advanced Git {-}

# Conflicts

**Key terms/commands:**

* **Conflict**: when the same portion of a file is edited, it will have to be manually resolved before it can be pulled/pushed.

## Create a conflict

Go into your fake collaborator's folder and add a line to `foo.txt`.

```{r echo=F}
# Change directory into workdir so the rest of the bash commands will be run in it
knitr::opts_knit$set(root.dir="~/workdir_fake_collab")
```

```{bash}
cd ~/workdir_fake_collab
echo fake_colab >> foo.txt
```

Add & commit your change.

```{bash}
git add foo.txt

git commit -m "Add fake collab line to foo.txt"
```

Push the change to the remote repository
`git push`

Now go into the original `workdir` and add a different line to `foo.txt`
```{r echo=F}
# Change directory into workdir so the rest of the bash commands will be run in it
knitr::opts_knit$set(root.dir="~/workdir")
```

```{bash}
cd ~/Desktop/workdir

echo real_me >> foo.txt
```

Add and commit the change

```{bash}
git add foo.txt

git commit -m "Add real me line to foo.txt"

```

Try to push it, and you should get an error

`git push`

## Resolving a conflict

Pull the changes from the remote server, which your fake collab has made a change

`git pull`

This should result in a conflict message. Two versions of the conflicting line is shown: 

* Your local version is between <<<<<<< HEAD` and `=======`
* The remote version is between `=======` and `>>>>>>> (unique identifier of the commit)`

Edit the file with conflicting lines

`nano foo.txt`

Then add and commit the edited file

```
git add foo.txt

git commit -m "Merge changes from Github"
```

Push your changes to the remote repo

`git push`

Now we pull from the remote repo again


## Tips to prevent conflicts

* Always fetch/merge (or pull) before making changes locally
* Use **branches** 
* Commit often (so people can pull your changes frequently as well)
* Have smaller files, so it is less likely for multiple people to edit the same file. 
* Communicate often with your collaborators :) 
