# (PART) Advanced Git {-}

# Conflicts

**Key terms/commands:**

* **Conflict**: when the same portion of a file is edited, it will have to be manually resolved before it can be pulled/pushed.

## Create a conflict

Go into your fake collaborator's folder and add a line to `foo.txt`.

```{r echo=F}
# Change directory into workdir so the rest of the bash commands will be run in it
knitr::opts_knit$set(root.dir="~/workdir_fake_collab")
```

```{bash}
cd ~/workdir_fake_collab
echo fake_colab >> foo.txt
```

Add & commit your change.

```{bash}
git add foo.txt
git commit -m "Add fake collab line to foo.txt"
```

Push the change to the remote repository

```{bash, eval = FALSE}
git push origin master
```


```
## Counting objects: 3, done.
## Delta compression using up to 8 threads.
## Compressing objects: 100% (2/2), done.
## Writing objects: 100% (3/3), 328 bytes | 328.00 KiB/s, done.
## Total 3 (delta 0), reused 0 (delta 0)
## To github.com:your_name/workdir.git
   09aba9d..d36beb6  master -> master
```

Now go into the original `workdir` and add a different line to `foo.txt`
```{r echo=F}
# Change directory into workdir so the rest of the bash commands will be run in it
knitr::opts_knit$set(root.dir="~/workdir")
```

```{bash}
cd ~/workdir
echo real_me >> foo.txt
```

Add and commit the change

```{bash}
git add foo.txt
git commit -m "Add real me line to foo.txt"
```

Try to push it, and you should get an error

```{bash, eval = FALSE}
git push origin master
```

```
## To github.com:mychan24/tmp.git
##  ! [rejected]        master -> master (fetch first)
## error: failed to push some refs to 'git@github.com:your_name/workdir.git'
## hint: Updates were rejected because the remote contains work that you do
## hint: not have locally. This is usually caused by another repository pushing
## hint: to the same ref. You may want to first integrate the remote changes
## hint: (e.g., 'git pull ...') before pushing again.
## hint: See the 'Note about fast-forwards' in 'git push --help' for details.
```

* Note that if you have get an error from Git, it tries to give you hints on how to fix the error. 
* It tells you that there is something in the remote repo. It suggests that you should integrate changes first by using `git pull`. 

## Resolving a conflict

Pull the changes your fake collaborator made in the remote server

```{bash, eval = FALSE}
git pull
```

```
## remote: Enumerating objects: 5, done.
## : Counting objects: 100% (5/5), done.
## remote: Compressing objects: 100% (2/2), done.
## remote: Total 3 (delta 0), reused 3 (delta 0), pack-reused 0
## Unpacking objects: 100% (3/3), done.
## From github.com:mychan24/tmp
##    09aba9d..d36beb6  master     -> origin/master
## Auto-merging foo.txt
## CONFLICT (content): Merge conflict in foo.txt
## Automatic merge failed; fix conflicts and then commit the result.
```

The output shows there is a **Conflict Message**! 

When this situation happens, Git will merge the conflicting changes into the file in question (i.e., `foo.txt`), and tells you that manual interventoin is needed.


### Look at the file with conflict and understanding the conflict message

```{bash, eval = FALSE}
cat foo.txt
```

```
## hello
## world
## <<<<<<< HEAD
## real_me
## =======
## fake_collab
## >>>>>>> d36beb66cb58e2e096964e5677adfdde5c1889ee
```

* The conflicted portion of the file is indicated by `<<<<<<<` and `=======`
  + Changes you made in your **local copy** is between `<<<<<<< HEAD` and `=======`
  + Changes from the **remote copy** is between `=======` and `>>>>>>> <commit identifier>`

Manually edit the file using a text editor (here we use `nano`) to the state where you want the file to be.

```{bash, eval = FALSE}
nano foo.txt
```

Make the resulting file look like this:

```{bash, include =F}
printf "hello\nworld\nwhales are good\n" > foo.txt
```

```
hello
world
whales are good
```

Add and commit the edited file

```{bash}
git add foo.txt
git commit -m "Merge changes from Github, whales are good"
```

Push your changes to the remote repo

```{bash, eval = FALSE}
git push
```

```
## Counting objects: 6, done.
## Delta compression using up to 8 threads.
## Compressing objects: 100% (4/4), done.
## Writing objects: 100% (6/6), 638 bytes | 638.00 KiB/s, done.
## Total 6 (delta 0), reused 0 (delta 0)
## To github.com:your_name/workdir.git
##    d36beb6..0f2d252  master -> master
```

Now your fake collaborator can `pull` from the remote repo again

```{bash, eval = FALSE}
cd ~/workdir_fake_collab
git pull
```

```
## remote: Enumerating objects: 10, done.
## remote: Counting objects: 100% (10/10), done.
## remote: Compressing objects: 100% (4/4), done.
## remote: Total 6 (delta 0), reused 6 (delta 0), pack-reused 0
## Unpacking objects: 100% (6/6), done.
## From github.com:mychan24/tmp
##    d36beb6..0f2d252  master     -> origin/master
## Updating d36beb6..0f2d252
## Fast-forward
##  foo.txt | 2 +-
##  1 file changed, 1 insertion(+), 1 deletion(-)
```

Both you and your fake collaborator now have the updated `foo.txt`. Check by printing the file

```{bash}
cat foo.txt
```

## Tips to prevent conflicts

* Always fetch/merge (or pull) before making changes locally
* Use **branches** (see upcoming chapter)
* Commit often (so people can pull your changes frequently as well)
* Have smaller files, so it is less likely for multiple people to edit the same file. 
* Communicate often with your collaborators :) 

***
**You have now resolved conflicted commits on git. Follow the tips above and hopefully you don't have to do this often.**
